Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-05-21 analysis/paper/paper.Rmd
Correct file save for figure 2

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_1.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_2.eps"))
```

>>>>

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Figure_2.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Figure_2.eps"))
```
